final_project_draft

### 2022-04-18 draft.Rmd
April 18th graded after class commit. Continued modifying visualizations and working on new ideas.

ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 5),
        legend.text = element_text(family = "mono",
                                   size = 5),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9),
        legend.box.background = element_rect())

ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  geom_point(data = average_donation, aes(x = mean, colour = "Mean Donations")) +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
  scale_colour_manual(values = c("Mean Donations" = "red")) +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 7),
        legend.text = element_text(family = "mono",
                                   size = 6),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9,
                                     vjust = 5),
        legend.box.just = "left",
        legend.box.background = element_rect())

ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  geom_point(data = average_donation, aes(x = mean, colour = "Mean Donations")) +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_viridis_d() +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 7),
        legend.text = element_text(family = "mono",
                                   size = 6),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9,
                                     vjust = 5),
        legend.box.just = "left",
        legend.box.background = element_rect())

@@

frequent %>% mutate(party = fct_relevel(Party, c("Republican", "Democrat", 
                                      "Bipartisan, but mostly Republican", 
                                      "Bipartisan", "N/A",
                                      "Bipartisan, but mostly Democratic",
                                      "Independent", 
                                      "Mean Donations")))

sum_donations <- frequent %>% group_by(Owner) %>%
  summarise(sum = sum(amount)) %>%
  rename(Sum = 'sum') %>%
  arrange(desc(Sum))
sum_donations

@@

 cj_party <- charles_johnson %>% group_by(Party) %>%
  summarise(n = n()) %>%
  mutate(party = fct_reorder(.f = Party, .x = n)) %>%
   mutate(Party = fct_relevel(party, c("Democrat", "Bipartisan, but mostly Republican", "Republican")))

@@

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  scale_fill_viridis_d(option = "inferno") +
  labs(title = "Party Affiliation of Political Donations Made by Charles Johnson",
       x = " ",
       y = " ") +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  hjust = 0.5,
                                  size = 13,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_text(family = "mono",
                                    size = 9,
                                    face = "italic",
                                    margin = margin(t = 20)),
        axis.title.y = element_text(family = "mono",
                                    margin = margin(t = 20, b = 20, r = 20)))

@@

ggplot(data = recipients, aes(x = recipient, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  labs(x = " ",
       y = "Count of Donations") +
  labs(title = "Organizations Receiving Most Donations Among All Owners") +
  scale_fill_brewer(palette = "Dark2") +
  theme(legend.position = "bottom") +
  scale_x_discrete(labels = new_names) +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono",
                                  size = 8),
        axis.title.x = element_text(size = 10,
                                    margin = margin(t = 20,
                                                    b = 10)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
         legend.box.background = element_rect())

@@

ggplot(data = top10, aes(x = order, y = NetWorth, fill = Industry)) +
  geom_col() +
  coord_flip() +
  labs(x = "Billionaire Name", 
       y = "Net Worth",
       caption = "Measured in Billions",
       colour = "Industry",
       title = "2021 Forbes Billionaires with the Highest Net Worth") +
  scale_fill_viridis_d() +
  scale_x_discrete(labels = new_names2) +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono",
                                   face = "italic"),
        plot.caption = element_text(family = "mono",
                                    face = "italic"))
```

@@

filter <- countries_10 %>% filter(!is.na(age))
filter
filter2 <- filter %>% group_by(Country) %>%
  summarise(Average = mean(age)) %>%
  mutate(order = fct_reorder(.f = Country, .x = Average))
filter2

ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point(alpha = 0.4) +
  coord_flip() +
  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age"),
             size = 2.5) +
  scale_colour_manual(values = c("Mean Age" = "red")) +
  labs(x = "Country", 
       y = "Age",
       title = "Average Age of Billionaires by Country",
       caption = "The Red Points Indicate the Average Age of Billionaires From Each
       Country") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "italic"),
        legend.position = "none",
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic")) +
  geom_label_repel(data = check, aes(label = age, family = "mono"))
```

@@

ggplot(data = above_or_below_us, aes(x = order, y = networth, colour = above_avg)) +
  geom_segment(aes(x = order, xend = order, y = avg, yend = networth)) +
  geom_point() +
  coord_flip() +
  labs(x = "Name",
      y = "Net Worth",
      colour = "Average") +
  theme(axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"),
        legend.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono"),
        axis.ticks = element_blank())
```

@@

## Playing Around with New Variables 
```{r}
self_made <- forbes_billionaires %>% group_by(Self_made) %>%
  summarise(n = n())

@@

@@

ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
  geom_jitter(alpha = 0.4) +
  coord_flip() +
  labs(x = "Education Level",
       y = "Net Worth")
```

>>>>

ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 5),
        legend.text = element_text(family = "mono",
                                   size = 5),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9),
        legend.box.background = element_rect())
```

## Only average - no political party 
``` {r}
ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  geom_point(data = average_donation, aes(x = mean, colour = "Mean Donations")) +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
  scale_colour_manual(values = c("Mean Donations" = "red")) +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 7),
        legend.text = element_text(family = "mono",
                                   size = 6),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9,
                                     vjust = 5),
        legend.box.just = "left",
        legend.box.background = element_rect())
```

## With average but no way to distinguish
```{r}
ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  geom_point(data = average_donation, aes(x = mean, colour = "Mean Donations"))+
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_viridis_d() +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 7),
        legend.text = element_text(family = "mono",
                                   size = 6),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9,
                                     vjust = 5),
        legend.box.just = "left",
        legend.box.background = element_rect())

@@

frequent %>% mutate(party = fct_relevel(Party, c("Republican", "Democrat", 
                                      "Bipartisan, but mostly Republican", 
                                      "Bipartisan", "N/A",
                                      "Bipartisan, but mostly Democratic",
                                      "Independent", 
                                      "Mean Donations")))
```

## sum of all donations
```{r}
sum_donations <- frequent %>% group_by(Owner) %>%
  summarise(sum = sum(amount)) %>%
  rename(Sum = 'sum') %>%
  arrange(desc(Sum))
sum_donations

@@

 cj_party <- charles_johnson %>% group_by(Party) %>%
  summarise(n = n()) %>%
  mutate(party = fct_reorder(.f = Party, .x = n)) %>%
   mutate(Party = fct_relevel(party, c("Republican", "Bipartisan, but mostly Republican", "Democrat")))

@@

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  scale_fill_brewer(palette= "Pastel2") +
  labs(title = "Party Affiliation of Political Donations Made by Charles Johnson",
       x = " ",
       y = " ") +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  hjust = 0.5,
                                  size = 13,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_text(family = "mono",
                                    size = 9,
                                    face = "italic",
                                    margin = margin(t = 20)),
        axis.title.y = element_text(family = "mono",
                                    margin = margin(t = 20, b = 20, r = 20)))

@@

ggplot(data = recipients, aes(x = recipient, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  labs(x = " ",
       y = "Count of Donations") +
  labs(title = "Organizations Receiving Most Donations Among All Owners") +
  scale_fill_brewer(palette = "Accent") +
  theme(legend.position = "bottom") +
  scale_x_discrete(labels = new_names) +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 7),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono",
                                  size = 8),
        axis.title.x = element_text(size = 10,
                                    margin = margin(t = 10,
                                                    b = 10)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
         legend.box.background = element_rect())

@@

ggplot(data = top10, aes(x = order, y = NetWorth, fill = Industry)) +
  geom_col() +
  coord_flip() +
  labs(x = "Billionaire", 
       y = "Net Worth",
       caption = "Measured in Billions",
       colour = "Industry",
       title = "2021 Forbes Billionaires with the Highest Net Worth") +
  scale_fill_viridis_d() +
  scale_x_discrete(labels = new_names2) +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 30,
                                                    b = 30))),
        legend.box.spacing = unit(0.5, 'cm'),
        axis.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 15,
                                                    b = 15,
                                                    vjust = 15))),
        legend.margin = margin(c(t = 30)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono",
                                   face = "italic"),
        plot.caption = element_text(family = "mono",
                                    face = "italic",
                                    vjust = 45,
                                    hjust = 0.5,
                                    margin = margin(c(t = 30,
                                                      b = 30))),
        legend.key.size = unit(.3, 'cm'))
```

@@

filter <- countries_10 %>% filter(!is.na(age))
filter
filter2 <- filter %>% group_by(Country) %>%
  summarise(Average = mean(age)) %>%
  mutate(order = fct_reorder(.f = Country, .x = Average))
filter3 <- filter2 %>% rename(age = 'Average')
```

## Outliers labeled 
```{r}
ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point(alpha = 0.4) +
  coord_flip() +
  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age of Billionaires"),
             size = 2.5) +
  scale_colour_manual(values = c("Mean Age of Billionaires" = "red")) +
  labs(x = "Country", 
       y = "Age",
       title = "Average Age of Billionaires by Country") +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "italic"), 
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic")) 
```

## Average labeled 
```{r}
ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point(alpha = 0.4) +
  coord_flip() +
  geom_label(data = filter3, aes(label = age)) +
  scale_colour_manual(values = c("Mean Age" = "red")) +
  labs(x = "Country", 
       y = "Age",
       title = "Average Age of Billionaires by Country") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "italic"),
        legend.position = "none",
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic")) 
```

@@

ggplot(data = above_or_below_us, aes(x = order, y = networth, colour = above_avg)) +
  geom_segment(aes(x = order, xend = order, y = avg, yend = networth)) +
  geom_point() +
  coord_flip() +
  labs(x = "Name",
      y = "Net Worth",
      caption = "Measured in Billions",
      colour = "Average",
      title = "Billionaires In The Fashion Industry",
      subtitle = "Do these billionaires fall above or below the average billionaire net worth in the U.S.?") +
  theme(axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"),
        legend.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono"),
        plot.caption = element_text(family = "mono",
                                    hjust = 0.5),
        plot.title = element_text(family = "mono"),
        plot.subtitle = element_text(family = "mono"),
        axis.ticks = element_blank())
```

@@

## Playing Around with New Variables - looking at self made billionaires, education level of billionaires 
```{r}
self_made <- forbes_billionaires %>% group_by(Self_made) %>%
  summarise(n = n())

@@

harvard <- tidy_education %>% filter(University == "Harvard University")
harvard

## should do something with this to show the degree, self_made, networth, etc.

@@

ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
  geom_jitter(alpha = 0.4) +
  coord_flip() +
  labs(x = "Education Level",
       y = "Net Worth")

ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
  geom_violin() +
  coord_flip()

library(ggridges)
ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
  geom_density_ridges()
```
